---
title: "Data Science 1 - Midterm Project"
author: "Adam Haertter & Brennan Mulligan"
format: pdf
---

# The Assignment

## Midterm - Open Case Studies Exploration

### Open Case Studies

The Open Case Studies (OCS) project is an educational resource of experiential guides that demonstrate how to effectively derive knowledge from data in real-world challenges. This project is the result of work of a team of researchers from Johns Hopkins University and it's Principal Investigator Dr. Stephanie Hicks. The project contains 12 different case studies. You can check out the projects and case studies here: https://www.opencasestudies.org/.

### Midterm Tasks

For the midterm, you are going to you are going to choose a case study that you want to work with (from the approved list that is listed) below and complete a number of tasks. Specifically,

1.  You need to choose a case study to work with. Here are the list of approved case studies:

-   School Shootings in the United States
-   Opioids in United States
-   Mental Health of American Youth
-   Exploring CO2 emissions across time
-   Exploring global patterns of dietary behaviors associated with health risk

2.  Complete the case study. The studies are really well documented and includes all of the requisite code you will need. You will already know some of the skills from class, but each study contains some new skills. Write down your work in a Quarto document. Make sure to answer all of the questions they ask throughout. The answers are included, but try to answer the questions before you look at the key.

3.  Answer the suggested homework question(s) in the same Quarto document you did #2 in.

4.  Come up with your own question and answer it. Your question should be a "big picture" question, not one that can be answered with a single plot or summary table.

------------------------------------------------------------------------

# The Process & Analysis

> (Our answers start here)

## Choosing an Open Case Study

For our open case study, we have chosen to analyze the [Mental Health of American Youth](https://www.opencasestudies.org/ocs-bp-youth-mental-health/), chosen from the provided list of [Open Case Studies](https://www.opencasestudies.org/#searchtab).

The main questions the case study intends to follow are:

1.  How have depression rates in American youth changed since 2004, according to the NSDUH data? How have rates differed between different youth subgroups (age, gender, ethnicity)?

2.  Do mental health services appear to be reaching more youths? Again, how have rates differed between different youth subgroups (age, gender, ethnicity)?

```{r lib}
#| message: false 
#| echo: false

library(here)
library(rvest)
library(dplyr)
library(magrittr)
library(stringr)
library(tidyr)
library(tibble)
library(purrr)
library(ggplot2)
library(directlabels)
library(scales)
library(forcats)
library(ggthemes)
library(rstatix)
library(cowplot)
library(OCSdata)
library(readr)

```

## Following the Case Study

### Data Import

Following the case study, data should be obtained by scraping the web. Specifically, we need to scrape the [NSDUH survey](https://www.samhsa.gov/data/sites/default/files/cbhsq-reports/NSDUHDetailedTabs2018R2/NSDUHDetTabsSect11pe2018.htm) site.

```{r}
# Data Import
table11.1a <- read_html("https://www.samhsa.gov/data/sites/default/files/cbhsq-reports/NSDUHDetailedTabs2018R2/NSDUHDetTabsSect11pe2018.htm") %>%
  html_nodes(xpath = "/html/body/div[4]/div[1]/table") %>%
  html_table() %>%
  .[[1]]

# Defining a scraper function
scraper <- function(XPATH) {
  NSDUH_url <- "https://www.opencasestudies.org/ocs-bp-youth-mental-health/data/raw/samhsa.gov_2020_tables.htm"
  table <- NSDUH_url %>%
    read_html() %>%
    html_nodes(xpath = XPATH) %>%
    html_table()
  output <- table[[1]]
  output
}

# Scraping the rest of the tables
table11.1b <- scraper(XPATH = "/html/body/div[4]/div[2]/table")
table11.2a <- scraper(XPATH = '/html/body/div[4]/div[3]/table')
table11.2b <- scraper(XPATH = '/html/body/div[4]/div[4]/table')
table11.3a <- scraper(XPATH = '/html/body/div[4]/div[5]/table')
table11.3b <- scraper(XPATH = '/html/body/div[4]/div[6]/table')
table11.4a <- scraper(XPATH = '/html/body/div[4]/div[7]/table')
table11.4b <- scraper(XPATH = '/html/body/div[4]/div[8]/table')

# Saving the data locally
save(table11.1a, table11.1b, table11.2a, table11.2b, 
     table11.3a, table11.3b, table11.4a, table11.4b, 
     file = here("data", "imported", "imported_data.rda"))

```

### Data Wrangling

```{r}
# Data Wrangling
load(file = here::here("data", "imported", "imported_data.rda"))

# Separating the legend
legend <- table11.1a %>%
  as_tibble() %>%
  select(`2004`) %>%
  tail(n = 1)

table11.1a %<>%
  as_tibble() %>%
  slice(1:(n()-1))

#slice_head(table11.1a, n = (length(pull(table11.1a, `2002`))))
#pull(legend, `2004`)

# Unifying the NA values based on the legend
table11.1a %<>%
  mutate_all(~na_if(., "nc")) %>%
  mutate_all(~na_if(., "--")) %>%
  mutate_all(~na_if(., "")) %>%
  mutate_all(~na_if(., "*"))

#head(table11.1a)
#colnames(table11.1a)

# Cleaning up the row names
table11.1a %<>%
  rename(MHS_setting = `Setting Where Mental Health ServiceWas Received`)

#head(table11.1a)
#table11.1a %>% pull(MHS_setting)

table11.1a %<>%
  mutate(MHS_setting = 
           str_remove_all(string = MHS_setting,
                          pattern = "[:digit:]|\r\n|[:punct:]|")) %>%
  mutate(MHS_setting = 
           str_replace_all(string = MHS_setting,
                           pattern = "[:blank:]{1,}",
                           replacement = " "))

# Cleaning up numerical values
table11.1a %<>%
  mutate(across(.cols = -MHS_setting,
                str_remove_all,
                "a|,")) %>%
  mutate(across(.cols = -MHS_setting,
                as.numeric))

# Type, subtype, and short labels
table11.1a %<>%
  mutate(type = c(rep("Specialty", 9), 
                  rep("Nonspecialty", 11))) %>%
  mutate(subtype = c("Specialty_total", 
                     rep("Outpatient", 5), 
                     rep("Inpatient", 3), 
                     "Nonspecialty_total", 
                     rep("Education", 3), 
                     rep("General_medicine", 2),
                     rep("Juvenile_Justice", 2), 
                     rep("Child_Welfare", 2), 
                     "combination")) %>%
  mutate(short_label = c("Specialty total", 
                         "Outpatient total", 
                         "Therapist", 
                         "Clinic", 
                         "Day program",
                         "In-home Therapist", 
                         "Inpatient total", 
                         "Hospital", 
                         "Residential Center",
                         "Nonspecialty total", 
                         "School total", 
                         "School Therapist", 
                         "School Program", 
                         "General Medicine",
                         "Family Dr",
                         "Justice System",
                         "Justice System",
                         "Welfare", 
                         "Fostercare", 
                         "Specialty Combination"))

# Filtering out empty rows
table11.1a %<>%
  filter(MHS_setting != "General_Medicine") %>%
  filter(MHS_setting != "Juvenile_Justice") %>%
  filter(MHS_setting != "Child_Welfare")
  
head(table11.1a)
dim(table11.1a)

# Pivoting data
table11.1a %<>%
  tidyr::pivot_longer(cols = contains("20"), 
                      names_to = "Year",
                      values_to = "Number") %>%
  mutate(Year = as.numeric(Year))

dim(table11.1a)
head(table11.1a)
```

#### Question Opportunity:

Why do we have 340 rows now?

**Answer**: We now have 340 rows because we have pivoted the table to be longer. Previously, the dimensions were 20 x 21, and after the pivot the dimensions are 340 x 6. The number 340 comes from the fact that all of the columns corresponding to years (2002 to 2018) are now each their own rows, with the other columns being preserved. There are 17 of these columns, each with 20 rows before the pivot. Because each of these now becomes its own row, we can see where the new row number comes from: $$17 * 20 = 340$$

Continuing with the data wrangling, we can wrap these previous steps into a singular function which will then be applied to Table 11.1b.

```{r}
# Continue Data Wrangling

# Defining a similar summary function for future
# This just requires retracing the same steps as above
data_prep_settings <- function(TABLE, new_col, pivot_col){
  # Convert to tibble
  as_tibble(TABLE) %>%
  # Remove last row
  slice(1:(n() - 1)) %>%
  # Convert bad values to NA
  mutate_all(~na_if(., "nc")) %>%
  mutate_all(~na_if(., "--")) %>%
  mutate_all(~na_if(., "")) %>%
  mutate_all(~na_if(., "*")) %>%
  # Rename column
  rename({{new_col}} := names(.)[1]) %>%
  # Clean unwanted characters out
  mutate({{new_col}} := 
        str_remove_all(string = pull(., {{new_col}}), 
                        pattern = "[:digit:]|\r\n|[:punct:]|")) %>%
  mutate({{new_col}} := 
        str_replace_all(string =pull(., {{new_col}}),
                         pattern = "[:blank:]{1,}", 
                         replacement = " ")) %>%
  mutate(across(.cols = -{{new_col}},
                       stringr::str_remove_all, "a|,")) %>%
  # Make columns numeric where applicable
  mutate(across(-{{new_col}}, as.numeric)) %>%
  # Add new variables
  mutate(type = c(rep("Specialty", 9), rep("Nonspecialty", 11))) %>%
  mutate(subtype = c("Specialty_total",
                       rep("Outpatient", 5),
                       rep("Inpatient", 3),
                       "Nonspecialty_total",
                       rep("Education", 3),
                       rep("General_medicine", 2),
                       rep("Juvenile_Justice", 2),
                       rep("Child_Welfare", 2),
                       "combination")) %>% 
  mutate(short_label = c("Specialty total", "Outpatient total",  
                           "Therapist", "Clinic", "Day program", 
                           "In-home Therapist", "Inpatient total",
                           "Hospital", "Residential Center",
                           "Nonspecialty total", "School total", 
                           "School Therapist", "School Program", 
                           "General Medicine", "Family Dr", 
                           "Justice System", "Justice System", 
                           "Welfare", "Fostercare", 
                           "Specialty Combination")) %>%
  # Remove majority NA rows
  filter(rowSums(is.na(select(., is.numeric))) <
           length(select(., is.numeric))) %>%
  # Reformat table
  pivot_longer(cols = contains("20"),
               names_to = "Year", 
               values_to = pivot_col)%>%
  mutate(Year = as.numeric(Year))
}

# Applying the transformation 11.1b
table11.1b <- data_prep_settings(TABLE = table11.1b, 
                   new_col = "MHS_setting",
                   pivot_col = "Percent")

# Defining function for demographic tables
data_dem_settings <- function(TABLE){
  # Convert to tibble
  as_tibble(TABLE) %>%
  # Remove the last row
  slice(1:(n()-1)) %>%
  # Convert bad values to NA
  mutate_all(~na_if(., "nc")) %>%
  mutate_all(~na_if(., "--")) %>%
  mutate_all(~na_if(., "")) %>%
  mutate_all(~na_if(., "*")) %>%
  # Rename the first column to be "Demographic"
  rename(Demographic := names(.)[1]) %>%
  # Replace unwanted characters
  mutate(Demographic := str_replace_all(string = pull(., Demographic),
                                        pattern = "[:blank:]{1,}", 
                                        replacement = " ")) %>%
  mutate(Demographic = str_replace(string = Demographic, 
                                   pattern = "1", 
                                   replacement = "Age: 1")) %>%
  # Create new variable
  mutate(subgroup = c("Total", rep("Age", 4), 
                    rep("Gender", 3), rep("Race/Ethnicity", 9))) %>%
  # Remove "a" from numbers
  mutate(across(.cols = contains("20"),
                       stringr::str_remove_all, "a|,")) %>%
  # Convert to numeric
  mutate(across(contains("20"), as.numeric)) %>%
  # Remove majority NA rows
  filter(rowSums(is.na(select(., is.numeric))) < length(select(., is.numeric)))
}

# Applying table format to other tables
table11.2a <- data_dem_settings(TABLE = table11.2a)
table11.2b <- data_dem_settings(TABLE = table11.2b)
table11.3a <- data_dem_settings(TABLE = table11.3a)
table11.3b <- data_dem_settings(TABLE = table11.3b)
table11.4a <- data_dem_settings(TABLE = table11.4a)
table11.4b <- data_dem_settings(TABLE = table11.4b)

# Assigning data_type
table11.2a %<>% mutate(data_type = "Major_Depressive_Episode")
table11.2a %<>% mutate(data_type = "Major_Depressive_Episode")
table11.2b %<>% mutate(data_type = "Major_Depressive_Episode")
table11.3a %<>% mutate(data_type = "Severe_Major_Depressive_Episode")
table11.3b %<>% mutate(data_type = "Severe_Major_Depressive_Episode")
table11.4a %<>% mutate(data_type = "Treatment")
table11.4b %<>% mutate(data_type = "Treatment")

# Checking the data formats
data_dem_check <- function(TABLE){
  results <- tibble(
    tibble_check = case_when(is_tibble(TABLE) ~ "Good!",
                             TRUE ~ "Not a tibble"),
    legend_check = case_when(TABLE %>% 
                               slice(n()) %>% 
                               pull(`2018`) %>%
                               str_detect(pattern = "--")  ~ "Legend might still be there",
                             TRUE ~ "Good!"),
    NAs_check = case_when(any(str_detect(TABLE, pattern = "nc")) 
                          ~ "NA not fixed",
                          TRUE ~ "Good!"),
    firstcol_check = case_when(names(TABLE)[1] == "Demographic" 
                               ~ "Good!",
                               TRUE ~ "check first column"),
    white_space_check = case_when(any(str_detect(TABLE, pattern = "[:blank:]{2,}")) 
                                  ~ "white spaces not fixed",
                                  TRUE ~ "Good!"),
    age_data_check = case_when(any(str_detect(pull(TABLE, Demographic), pattern = "^1"))
                               ~ "Age data not fixed!",
                               TRUE ~ "Good!"),
    subgroup_check = case_when(any(names(TABLE) == "subgroup")
                               ~ "Good!",
                               TRUE ~ "No subgroup variable!"),
    a_comma_check = case_when(TABLE%>% select(-Demographic, -subgroup, -data_type) %>% 
                                map_df(~(str_detect(.x, pattern ="a|,"))) %>%
                                rowSums(na.rm = TRUE) %>% 
                                sum() == 0
                              ~ "Good!",
                              TRUE ~ "There may be commas or the letter a in the year columns!"),
    numeric_check = case_when(sum(map_dbl(TABLE, is.numeric))== sum(str_count(names(TABLE), "20"))
                              ~ "Good!",
                              TRUE ~ "Variables are not numeric!"),
    empty_row_check = case_when(nrow(TABLE %>%filter(rowSums(is.na(select(., is.numeric))) > 
                                                       length(select(., is.numeric)))) > 0 
                                ~ "There are empty rows ",
                                TRUE ~ "Good!"))
  
  ifelse(all(results == "Good!"),
         "Data looks good!", glimpse(results))
}

tables_to_check <- list(table11.2a, 
                       table11.2b, 
                       table11.3a, 
                       table11.3b, 
                       table11.4a, 
                       table11.4b)
tables_to_check %>% map(data_dem_check)

# Binding count data and percent data
counts <- bind_rows(table11.2a, table11.3a, table11.4a)
percents <- bind_rows(table11.2b, table11.3b, table11.4b)

counts %>% distinct(data_type)
percents %>% distinct(data_type)

counts %<>% pivot_longer(cols = contains("20"), 
                         names_to = "Year", 
                         values_to = "Number") %>%
            mutate(Year = as.numeric(Year))

percents %<>% pivot_longer(cols = contains("20"), 
                           names_to = "Year", 
                           values_to = "Percent") %>%
              mutate(Year = as.numeric(Year))

glimpse(counts)
glimpse(percents)

# Updating Demographics
percents %<>% mutate(Demographic = str_replace(string = Demographic, 
                                             pattern = "AIAN",
                                         replacement = "American Indian and Alaska Native"))

percents %<>% mutate(Demographic =  str_replace(string = Demographic,
                                             pattern = "NHOPI",
                                         replacement = "Native Hawaiian or Other Pacific Islander"))

counts %<>% mutate(Demographic = str_replace(string = Demographic, 
                                             pattern = "AIAN",
                                         replacement = "American Indian and Alaska Native"))

counts %<>% mutate(Demographic =  str_replace(string = Demographic, 
                                             pattern = "NHOPI",
                                         replacement = "Native Hawaiian or Other Pacific Islander"))

# Saving data
save(percents, counts, table11.1a, table11.1b, 
     file = here("data", "wrangled", "wrangled_data.rda"))
write_csv(percents, path = here("data", "wrangled", "percents.csv"))
write_csv(counts, path = here("data", "wrangled", "counts.csv"))
write_csv(table11.1a, path = here("data", "wrangled", "table11.1a.csv"))
write_csv(table11.1b, path = here("data", "wrangled", "table11.1b.csv"))

```

### Data Visualization

```{r}
# Data Visualization

# Load Wrangled Data from Previous Section
load(file = here::here("data", "wrangled", "wrangled_data.rda"))

# Major Depressive Episode Graph that emphasizes
# the increase after 2011 with a background change
MDE_total <- percents %>%
  filter(data_type == "Major_Depressive_Episode", 
         Demographic == "TOTAL") %>%
  mutate(Demographic = recode(Demographic, 
             "TOTAL" = "Percent of respondents with MDE")) %>%
  ggplot(aes(x = Year, y = Percent, group = Demographic)) +
    facet_wrap( ~ Demographic)+
    geom_rect(xmin = 2011, xmax = Inf,  
              ymin = -Inf, ymax = Inf,  
              fill = "light gray") +
    geom_line(aes(color = Demographic), size = 1.5) +
    scale_x_continuous(breaks = seq(2004, 2018, by = 1),
                       labels = seq(2004, 2018, by = 1),
                       limits = c(2004, 2018)) +
    labs(title = "The Rate of Youths Aged 12 to 17 Reporting Having a \n Major Depressive Episode (MDE) is Increasing")+
    theme_classic() +
    theme(axis.text.x = element_text(angle = 90),
          legend.position = "none",
          strip.background = element_rect(fill ="black"),
          strip.text = element_text(face = "bold", 
                                    size = 14, 
                                    color = "white")) +
    scale_color_manual(values = c("blue"))

MDE_total

# Saving our graph as PNG
save(MDE_total, file =here::here("plots", "MDE_total.rda"))
png(here::here("plots", "MDE_total.png"))
MDE_total
dev.off()
```

#### Question Opportunity

What do you expect will happen when if we had used the + symbol to add the geom_rect() function with MDE_total like so? Is that what you anticipated? Why or why not?

```{r}
MDE_total + 
  geom_rect(xmin = 2011, xmax = Inf,  
            ymin = -Inf, ymax = Inf,  
            fill = "light gray")
```

**Answer**: Before running it, I expect that the rectangle will probably not act
in the way that we want it to. I see now that the rectangle actually goes over
the line and so now we can't actually see anything past 2011. I anticipated
something like this would happen because if you're making the whole graph before
adding the background, then it layers on top of what was previously created.
This leads to situations like these. The code for graphs needs to act like a
cake where you layer tha elements in the right order so that you can see the
top as the end result in the way that you want.

Continuing the Data Visualization Section using filters and subgroups

```{r}
# This function helps keep a repetitive theme that we will use
ocs_theme <- function() {
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90),
        strip.background = element_rect(fill = "black"),
        strip.text = element_text(face = "bold",
                                  size = 14,
                                  color = "white"))
}

#Major Depressive Episode based on Age Range and Gender Subgroups
MDE_age_gender <- percents %>%
  filter(data_type == "Major_Depressive_Episode", 
         subgroup != "Race/Ethnicity", 
         Demographic != "TOTAL") %>%
  ggplot(aes(x = Year, y = Percent, color = Demographic)) +
    geom_line(aes(color = Demographic), size = 1) +
    scale_x_continuous(breaks = seq(2004, 2018, by = 1),
                       labels = seq(2004, 2018, by = 1),
                       limits = c(2004, 2018)) +
    labs(title = "Major Depressive Episode among Persons Aged 12 to 17",
         subtitle = "By Demographic Characteristics, Percentages, 2004-2018") +
    facet_wrap(~ subgroup) +
    ocs_theme()

MDE_age_gender

#Setting colors as variables
age_col_light <- c("#B79F00")
age_col<- c("#6BB100")
age_col_dark<- c("#00BD5F")
Female_col <-c("#F564E3")
Male_col <- c("#619CFF")

# Modify with different labels and font and colors
MDE_age_gender <- directlabels::direct.label(
  MDE_age_gender, 
  list(dl.trans(y = y + 0.38, x = x -0.1), 
       "far.from.others.borders",
       cex = .8, 
       fontface=c("bold"), 
       dl.move("Age: 14-15", x = 2007, y = 9.7))
  ) +
  scale_color_manual(values = c(age_col_light, 
                                age_col, 
                                age_col_dark, 
                                Female_col, 
                                Male_col))

MDE_age_gender
```

#### Question Opportunity:

Try to come up with the code for this plot on your own before you reveal it.

```{r}
MDE_age_gender <-
  percents %>%
  filter(data_type == "Major_Depressive_Episode", 
         subgroup != "Race/Ethnicity", 
         Demographic != "TOTAL") %>%
  ggplot(aes(x = Year, y = Percent, group = Demographic)) +
    geom_rect(xmin = 2011, xmax = Inf,  
              ymin = -Inf, ymax = Inf,  
              fill = "light gray") +
    geom_line(aes(color = Demographic), size =1) +
    scale_x_continuous(breaks = seq(2004, 2018, by=1),
                       labels = seq(2004, 2018, by=1),
                       limits = c(2004, 2018)) +
    labs(title = "Major Depressive Episode\namong Persons Aged 12 to 17",
         subtitle = "By Demographic Characteristics, Percentages, 2004-2018") +
    facet_wrap(~ subgroup) +
    ocs_theme()

MDE_age_gender <- direct.label(
  MDE_age_gender, 
  list(dl.trans(y = y +0.38, x = x -0.2), 
       "far.from.others.borders", 
       cex = .8,
       fontface = "bold",
       dl.move("Age: 14-15", x = 2008, y =10))
  ) + 
  scale_color_manual(values = c(age_col_light, 
                                age_col, 
                                age_col_dark, 
                                Female_col, 
                                Male_col))
MDE_age_gender
```

Continuing and Finishing Data Visualization

```{r}
# Saving the graph and finishing the Data Visualization
save(MDE_age_gender, file =here::here("plots", "MDE_age_gender.rda"))
png(here::here("plots", "MDE_age_gender.png"))
MDE_age_gender
while (!is.null(dev.list()))  dev.off()
```

### Data Analysis

```{r}
# Data Analysis
load(file = here::here("data", "wrangled", "wrangled_data.rda"))

# Set up chi squared data
chi_squared_11.2a <- counts %>%
  filter(data_type == "Major_Depressive_Episode") %>%
  filter(Year %in% c(2004, 2018)) %>%
  filter(Demographic %in% c("Male", "Female")) %>%
  mutate(Number = Number * 1000) # Data are in thousands
```

#### Question Opportunity:

Using what you just learned about pivot_wider() and select() and without scrolling up, try to come up with the code to do the wrangling for this data.

```{r}
chi_squared_11.2a %<>%
  select(Demographic, Year, Number) %>%
  pivot_wider(names_from = Year,
              names_prefix = "Year",
              values_from = Number)
```

Continuing on following the case study, we need to continue formatting data for the chi-squared test and run the first chi-squared test.

```{r}
# Continuing data analysis
chi_squared_11.2a %<>%
  tibble::column_to_rownames("Demographic")

chi_squared_11.2a

# Run the Chi-Squared test
chisq.test(chi_squared_11.2a)
```

#### Question Opportunity:
Using what you learned about the Chi-squared test, describe the results in reference to the null hypothesis.

__Answer__: Since the p-value is less than $2.2^{-16}$, we know that the p-value is extremely small. Without having out $\alpha$ significance level explicitly defined, we can assume that $\alpha = 0.05$. Our p-value is much smaller than $\alpha$, so we can reject the null-hypothesis in this case. If $H_0$: The variables are independent, then therefore we have evidence to reject this hypothesis, and evidence suggests that the variables are not, in fact, independent.

Continuing with the data analysis, we need to set up a test to describe the size of the association present.

```{r}
# Set up prop_test
prop_test(chi_squared_11.2a, 
          detailed = TRUE, 
          correct = TRUE) %>%
  glimpse()

# Run transposed table through prop_test
t(chi_squared_11.2a) %>%
  prop_test(detailed = TRUE, correct = TRUE) %>%
  glimpse()

# Cross-reference with similar plot for counts
MDE_age_gender_counts <-
  counts %>%
  filter(data_type == "Major_Depressive_Episode", 
         subgroup != "Race/Ethnicity", 
         Demographic != "TOTAL") %>%
  ggplot(aes(x = Year, y = Number, group = Demographic)) +
    geom_rect(xmin = 2011, xmax = Inf,  
              ymin = -Inf, ymax = Inf,  
              fill = "light gray") +
    geom_line(aes(color = Demographic), size =1) +
    scale_x_continuous(breaks = seq(2004, 2018, by=1),
                       labels = seq(2004, 2018, by=1),
                       limits = c(2004, 2018)) +
    labs(title = "Major Depressive Episode\namong Persons Aged 12 to 17",
         subtitle = "By Demographic Characteristics, Percentages, 2004-2018") +
    facet_wrap(~ subgroup) +
    ocs_theme()

MDE_age_gender_counts <- direct.label(
  MDE_age_gender_counts, 
  list(dl.trans(y = y +0.38, x = x -0.2), 
       "far.from.others.borders", 
       cex = .8,
       fontface = "bold",
       dl.move("Age: 14-15", x = 2008, y =10))
  ) + 
  scale_color_manual(values = c(age_col_light, 
                                age_col, 
                                age_col_dark, 
                                Female_col, 
                                Male_col))

MDE_age_gender_counts 

# Analysis of Severe MDE
chi_squared_11.3a <- counts %>%
  filter(data_type == "Severe_Major_Depressive_Episode", 
         Year %in% c(2006, 2018), 
         Demographic %in% c("Male","Female")) %>%
  mutate(Number = Number * 1000) %>%
  select(-data_type, -subgroup) %>%
  pivot_wider(names_from = Year,
              names_prefix = "Year", 
              values_from = Number) %>%
  column_to_rownames("Demographic")

chi_squared_11.3a

# Running Chi-Squared test for 11.3a
chisq.test(chi_squared_11.3a)

t(chi_squared_11.3a) %>% 
  prop_test( detailed = TRUE, correct = TRUE) %>%
  glimpse()

```

#### Question Opportunity:

Try performing the same wrangling as we did for the percentage of each demographic that reported having a major depressive episode for the data about treatment.

```{r}
# Setting up data for 11.4a

chi_squared_11.4a <- counts %>%
  filter(data_type == "Treatment", 
         Year %in% c(2004, 2018), 
         Demographic %in% c("Male","Female")) %>%
  mutate(Number = Number * 1000) %>%
  select(-data_type, -subgroup) %>%
  pivot_wider(names_from = Year,
              names_prefix = "Year", 
              values_from = Number) %>%
  column_to_rownames("Demographic")

chi_squared_11.4a

```

After this, we need to run the chi-squared test on this data for 11.4a.

```{r}
# Chi-Squared for 11.4a
chisq.test(chi_squared_11.4a)

t(chi_squared_11.4a) %>% 
  prop_test(detailed = TRUE, correct = TRUE) %>%
  glimpse()


# While not part of the case study, we wanted to save this new graph, too.
save(MDE_age_gender_counts, file =here::here("plots", "MDE_age_gender_counts.rda"))
png(here::here("plots", "MDE_age_gender_counts.png"))
MDE_age_gender_counts
while (!is.null(dev.list()))  dev.off()
```

### Summary

```{r}
# Summary

```

## Homework Questions

```{r}
# Suggested HW Questions

```

## Our Own Question

For our own question, we would like to examine **\[Write about this more\]**

```{r}
# Our Own Question

```
